Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

>>>>

We first define two hypotheses, $h_{0}$ or the null hypothesis which states that the two data samples come from the same distribution and $h_{a}$ or an alternative hypothesis which states that both sample data comes from two different distributions.

The K-S test will produce two values, \texttt{statistic} and \texttt{pvalue}. If the \texttt{pvalue} is less than the significant value, or alpha which can be selected from a certain constants,
then we can reject $h_{0}$ and accept $h_{a}$. If the \texttt{pvalue} is not less than significant value, then the next step is to compare the statistical value and critical value. Critical value itself is a point on the hypothesis that will be compared to the results of the statistical values to be used to reject or accept the null hypothesis. If the statistical value is greater than critical value, then we can reject $h_{0}$ and accept $h_{a}$ or meaning that the two data samples come from different distributions. However, if the statistical value is smaller than the critical value, we cannot reject $h_{0}$ or it means both sample data come from the same distribution.
